NYC Spatial Models - Comparison of Spatial Models With and Without Twitter Data

### 2019-12-16 analysis/sdm.Rmd
make the code visiable

```{r W, echo=FALSE}
# tracts %>% class
# neighbors <- poly2nb(tracts, queen = TRUE)
# neighbors %>% write_rds("../output/neighbors.rds")
neighbors <- read_rds("../output/neighbors.rds")
neighbors %>% class
W <- nb2listw(neighbours = neighbors, zero.policy = TRUE)
print(W, zero.policy = TRUE)
trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
```

>>>>

```{r W}
# tracts %>% class
# neighbors <- poly2nb(tracts, queen = TRUE)
# neighbors %>% write_rds("../output/neighbors.rds")
neighbors <- read_rds("../output/neighbors.rds")
neighbors %>% class
W <- nb2listw(neighbours = neighbors, zero.policy = TRUE)
print(W, zero.policy = TRUE)
trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
```
